Taxonomic level search

### 2023-03-20 workflow/notebooks/tax-search.Rmd
TODO: table showing # features at each tax level before/after mikropml::preprocess
Replot tax search performance

```{r tax-search_perf}
results_dat %>% 
  ggplot(aes(x = taxlevel, y = AUROC, color = set)) +
  geom_hline(yintercept = 0.5, linetype = 'dashed') +
  geom_boxplot() +
  facet_wrap(dataset~outcome)+#, nrow = 1) +
  theme_sovacool()
```

>>>>

```{r tax-search_perf}
results_dat %>% 
  ggplot(aes(x = taxlevel, y = AUROC, color = set)) +
  geom_hline(yintercept = 0.5, linetype = 'dashed') +
  geom_boxplot() +
  facet_wrap(dataset+method~outcome)+#, nrow = 1) +
  theme_sovacool()
```
